\thesistitle

### 2019-06-28 sattose/paper.tex
Changed type 3R description
The world is better off with good labels

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

@@

\subsection{Type 2 clones}
Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

@@

\subsection{Type 3 clones}
Type 3 clones are \textit{copied fragments with further modification (having added, removed or changed statements)} \cite{roy2007survey}. Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}. This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity \cite{sajnani2016sourcerercc} of statement-level similarity \cite{kamalpriya2017enhancing}.

@@

\subsubsection{Type 1R clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}. However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical. Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type. In such cases refactoring opportunities could be invalidated. Therefore, we propose an alternative definition of type 1 clones. We have named it ``type 1R clones''. The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses). Type 1R clones differ from type 1 clones as follows:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are functionally equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
\end{itemize}

\subsubsection{Type 2R clones}
Type 2 clones allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones can be harmful instead of helpful.

@@

\subsubsection{Type 3R clones}
Type 3 clones allow any change in statements (added, removed and changed statements). Many clone detection tools have implemented this type by introducing a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}. This similarity threshold entails that two fragments may differ by a certain percentage. This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. This is a tradeoff, as an added conditional block increases the complexity of the system. Because of that, we defined type 3R clones in such a way that they are directed towards finding clones that are worth this tradeoff. This entails the following:

@@

\subsection{Survey on Clone Detection Tools}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview.
\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged. Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

@@

\subsection{Clone detection results}
Currently, we have implemented two clone detection algorithms into CloneRefactor. The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}. The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}. The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.

@@

\subsubsection{Our results} \label{chap:ourmeasurements}
Table~\ref{table:relations} contains our results regarding the relations between clone instances. In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in section \ref{chap:type1clones}.

>>>>

\subsection{Type 1 clones} \label{sec:type1}
Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

@@

\subsection{Type 2 clones}\label{sec:type2}
Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

@@

\subsection{Type 3 clones}\label{sec:type3}
Type 3 clones are \textit{copied fragments with further modification (having added, removed or changed statements)} \cite{roy2007survey}. Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}. This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity \cite{sajnani2016sourcerercc} of statement-level similarity \cite{kamalpriya2017enhancing}.

@@

\subsubsection{Type 1R clones} \label{sec:type1r}
Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}. However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical. Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type. In such cases refactoring opportunities could be invalidated. Therefore, we propose an alternative definition of type 1 clones. We have named it ``type 1R clones''. The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses). Type 1R clones differ from type 1 clones as follows:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g. \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object). This way we can validate whether two method references, like method calls, are functionally equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
\end{itemize}

\subsubsection{Type 2R clones}\label{sec:type2r}
We tackle the previously outlined shortcomings of type 2R clones (see section We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored. Type 1R clones are a subset of type 2R clones. All rules that apply to type 1R clones also apply to type 2R clones. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold. Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types. As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.

Type 2 clones allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones can be harmful instead of helpful.

@@

\subsubsection{Type 3R clones}\label{sec:type3r}
Type 3 clones allow any change in statements (added, removed and changed statements). Many clone detection tools have implemented this type by introducing a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}. This similarity threshold entails that two fragments may differ by a certain percentage. This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. This is a tradeoff, as an added conditional block increases the complexity of the system. Because of that, we defined type 3R clones in such a way that they are directed towards finding clones that are worth this tradeoff.

Type 3R clones allow, different from type 2R clones, a gap between two clone classes of statements that are not cloned. The following rules apply to this gap:

@@

\subsection{Survey on Clone Detection Tools}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze a popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview.
\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged. Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{sec:type1}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

@@

\subsection{Clone detection results}
Currently, we have implemented two clone detection algorithms into CloneRefactor. The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}. The second algorithm implements our type 1R, as explained in section \ref{sec:type1r}. The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.

@@

\subsubsection{Our results} \label{chap:ourmeasurements}
Table~\ref{table:relations} contains our results regarding the relations between clone instances. In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in section \ref{sec:type1r}.

### 2019-06-28 sections/research.tex
Changed type 3R description
The world is better off with good labels

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

@@

\subsection{Type 3 clones}
Type 3 clones are \textit{copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}. This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.

@@

\subsection{Type 1R clones} \label{chap:type1rclones}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones). We check functional equality of two fragments by validating the equality of the fully qualified identifier for referenced types, methods and variables. Type 1R clones are a subset of type 1 clones.

@@

\subsection{Type 3R clones}
Type 3 clones allow any change in statements, often bounded by a similarity threshold. This means that type 3 clones allow the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. See figure \ref{fig:type3} for an example of such a clone.

@@

Type 1R: Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations.
Type 2R: Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
Type 3R: Allows any difference. When refactored, this difference must be wrapped in its own block, which entails a major tradeoff.

@@

\section{Suitability of existing Clone Detection Tools for detecting these clones}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools in order to expand them with the proposed types. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze at least one popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview. We analyzed this behavior using a set of control projects.
\item \textbf{TODO: Criterium.}\simon{TODO} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored. Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{chap:type1clones}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

@@

Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3).

>>>>

\subsection{Type 1 clones}\label{sec:type1}
Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

@@

\subsection{Type 3 clones}\label{sec:type3}
Type 3 clones are \textit{copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed. Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}. This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.

@@

\subsection{Type 1R clones} \label{sec:type1r}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones). We check functional equality of two fragments by validating the equality of the fully qualified identifier for referenced types, methods and variables. Type 1R clones are a subset of type 1 clones.

@@

\subsection{Type 3R clones}\label{sec:type3r}
Type 3 clones allow any change in statements, often bounded by a similarity threshold. This means that type 3 clones allow the inclusion of a statement that is not detected by type 1 or 2 clone detection. When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements. See figure \ref{fig:type3} for an example of such a clone.

@@

\textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that \
contains the code of both locations.
\textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
\textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.

@@

\section{Suitability of existing Clone Detection Tools for detecting these clones}
\label{ch:tool-overview}
We conducted a short survey on (recent) clone detection tools in order to expand them with the proposed types. The results of our survey are displayed in table~\ref{table:dettools}. We chose a set of tools that are open source and can analyze at least one popular object-oriented programming language. Next, we formulate the following four criteria by which we analyze these tools:
\begin{enumerate}
    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones. We want to perform an analysis on all clones in projects to get a complete overview. We analyzed this behavior using a set of control projects.
\item \textbf{TODO: Criterium.}\simon{TODO} We assembled a number of test projects to assess the validity of clone detection tools. On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored. Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{sec:type1}). Because of this, we want to use a clone detection tool that can analyze such structures.
\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}). To achieve this, the tool needs to be able to allow those threshold changes. This can be either through simple changes of the source code, or by using some configuration file.
\end{enumerate}

@@

Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3).
